Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-14 prop_letter.tex
small things

In the long version of this paper, we establish that QIVPMs become
classical IVPMs when the space of events includes only mutually
commuting events. The idea of the proof is as follows. Given a
subspace of commuting events $\events_C$, we can construct a partial
orthonormal basis by diagonalization and complete it to a full
orthonornal basis $\overline{\events_C}$. We then build a bijection
between the QIVPM on the set of projectors associated with this basis
and the set of classical events corresponding to this basis. This
correspondence leads to a crucial property in our setting.

>>>>

In the long version of this paper, we establish that QIVPMs become
classical IVPMs when the space of events includes only mutually
commuting events. The idea of the proof is as follows. Given a
subspace of commuting events $\events_C$, we can construct a partial
orthonormal basis by diagonalization and complete it to a full
orthonormal basis $\overline{\events_C}$. We then build a bijection
between the QIVPM on the set of projectors associated with this basis
and the set of classical events corresponding to this basis. This
correspondence leads to a crucial property in our setting.
